$\pi$ with leftovers: \\ a mechanisation in Agda

### 2020-04-28 paper/paper.tex
Minor terminology correction
Note to mention our Curry-style encoding (first semantics, then typing)

@@

We make use \emph{leftover typing}, a technique consisting of adding an \emph{output context of usages} to the usual \emph{input context of usages}.
This output context contains the leftovers: the multiplicities unused by the processes.
Crucially, this output context can then be used as the input context of the continuation process.
The typing rules are introduced in \S \ref{leftover-typing}.

>>>>

\todo{Mention that our semantics is prior to our typing (Curry-style)}

@@

We make use \emph{leftover typing}, a technique consisting of adding an \emph{output usage context} to the usual \emph{input usage context}.
This output context contains the leftovers: the multiplicities unused by the processes.
Crucially, this output context can then be used as the input context of the continuation process.
The typing rules are introduced in \S \ref{leftover-typing}.
